---
title: "Reference Data, Snapshots, Lineage and Controls"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reference Data, Snapshots, Lineage and Controls}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE,comment="#>")
library(financialAccountingEngine)
```

The package includes two synthetic profiles with all 19 canonical tables. The
bitemporal selector requires exactly one active official row for every business
key at both cut-offs.

```{r}
data <- load_reference_data("SMALL_SA_RETAIL_FIA")
selected <- select_snapshot(list(instruments=data$instruments),"2026-12-31",
                            "2026-09-02T12:00:00+02:00")
stopifnot(length(selected$instruments)==5)
```

The complete run exposes copies of results and lineage. Mutating an accessor's
return value does not alter the result object.

```{r}
result <- run_dataset(data)
controls <- get_controls(result)
stopifnot(length(controls)==28,
          all(vapply(controls,function(x)x$status=="PASS",logical(1))))
lineage <- get_lineage(result)
lineage[c("contract_version","policy_id","rule_set_id","run_id")]
```

The source metadata contains links and hashes but does not redistribute
standard texts or download anything when the package is loaded.

```{r}
sources <- get_sources()
stopifnot(all(!vapply(sources,function(x)x$redistributed,logical(1))))
```
