---
title: "Getting Started with Granular Accounting Calculations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with Granular Accounting Calculations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE,comment="#>")
```

The package exposes small deterministic formulas as well as a controlled
complete workflow. Rates are decimals, time is measured in years and money in
one call uses one currency.

```{r}
library(financialAccountingEngine)
discount_factor(0.05,1)
effective_interest_rate(1000,list(c(1,1100)))
component_ecl(0.02,100000,0.40,0.05,1)
```

Policy and model inputs remain explicit. The packaged policy has a fixed ID and
date rather than a floating "latest" value.

```{r}
policy <- get_policy()
policy[c("policy_id","reporting_date","past_due_sicr_days")]
get_formula("F-ECL-001")
```

The synthetic small profile runs entirely offline. `APPROVED_REFERENCE` means
the package controls passed; it is not an institutional approval.

```{r}
result <- run_dataset(load_reference_data("SMALL_SA_RETAIL_FIA"))
stopifnot(result$status == "APPROVED_REFERENCE")
get_metrics(result)[c("opening_gross_exposure","closing_allowance")]
```
