---
title: "Hedges, Journals, Disclosures and Reconciliation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Hedges, Journals, Disclosures and Reconciliation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE,comment="#>")
library(financialAccountingEngine)
```

Hedge functions require designation, eligibility, an economic relationship and
explicit lifecycle facts. They calculate reference entries but never post them.

```{r}
hedge <- list(relationship_id="H",hedge_type="CASH_FLOW",hedging_change=120,
  hedged_change=-100,hedge_ratio=1,target_hedge_ratio=1,
  hedging_instrument_eligible=TRUE,hedged_item_eligible=TRUE,
  risk_component_eligible=TRUE,designation_documented=TRUE,
  risk_management_objective="Manage cash-flow risk",designated=TRUE,
  economic_relationship=TRUE,credit_risk_dominates=FALSE,
  forecast_transaction_expected=TRUE)
measured <- measure_hedge(hedge)
measured[c("status","oci_effective","ineffectiveness_pnl")]
```

Reference journals balance by batch. Account mapping and posting approval are
institutional responsibilities.

```{r}
inst <- list(list(instrument_id="x",gross_amount=100,instrument_type="LOAN"))
ecl <- list(list(instrument_id="x",stage="STAGE_1",final_ecl=20))
journals <- build_journals(ecl,c(x=5),c(x="AMORTISED_COST"),inst)
stopifnot(abs(sum(vapply(journals,function(x)x$debit-x$credit,numeric(1))))<1e-12)
```

Disclosure aggregation computes coverage from aggregate amounts and keeps the
regulatory bridge outside the accounting calculation.
