---
title: "Staging, Scenario ECL and POCI"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Staging, Scenario ECL and POCI}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE,comment="#>")
library(financialAccountingEngine)
```

Staging consumes documented facts and policy thresholds. Credit impairment has
priority over SICR, and days-past-due presumptions remain subject to governed
rebuttal rather than being hard-coded as an automatic conclusion.

```{r}
facts <- list(instrument_id="loan-1",impairment_scope="GENERAL_ECL",
              days_past_due=35,rating_orig=3,rating_current=5)
stage <- assess_stage(facts)
stage[c("stage","stage_reason")]
```

Scenario ECL calculates each scenario before probability weighting. Stage 1
uses defaults within one year; lifetime stages use all supplied years.

```{r}
instrument <- list(instrument_id="loan-1",impairment_scope="GENERAL_ECL",
                   ecl_method="COMPONENT_PD_LGD_EAD",eir=.05,overlay=0)
pd <- list(list(scenario_id="base",year=1,marginal_pd=.02))
lgd <- list(list(scenario_id="base",year=1,lgd=.40))
ead <- list(list(scenario_id="base",year=1,ead=100000))
loss <- scenario_ecl(instrument,"STAGE_1",pd,lgd,ead,c(base=1))
stopifnot(abs(loss$summary$final_ecl-761.904761904762)<1e-8)
loss$details
```

POCI allowance movements remain signed so favourable changes are not converted
into ordinary positive loss allowances.

```{r}
poci_allowance_change(20,30)
```
